Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-30 cav2017/cav2017.tex
de-vectorized k in Fig 4

We next evaluate $\hat{X}^\# \models \phi_\mathit{safety}$.  If the
verification holds we have a solution, and exit the loop.  Otherwise, we
find a counterexample iteration $k$ and corresponding initial point $x_0$
for which the property does not hold, which we use to locally refine the
abstraction.  When the abstraction cannot be further refined, we provide
them to the {\sc abstract} phase.
%
%\todo{we should have a better argument here.}
%\end{enumerate} 
\item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
  in which case we must refine the abstraction used by the synthesizer.
\begin{enumerate}
\item Find the constraints that invalidate the property
 as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum i.e., transfer function) of the closed loop dynamics. 
\item We use $\phi_\Lambda$ to
  further constrain the characteristic polynomial  
$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$. These constraints correspond to specific iterations for which the system may be unsafe.
\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $\vec{k}$ to the {\sc synthesize} phase.
  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
\end{enumerate} 
\end{enumerate}

@@

\begin{figure}
\centering
{\scriptsize
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ 
   \&
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
      \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
   \&
   \& complexnode/.pic={
     \coordinate (UNSAT);
     \coordinate (KUNSAT)  at ([xshift=0cm]UNSAT.center);
     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT\\ (No Candidate Found)};
  }
  \& \& \coordinate (FAIL);\\
  };
  \path
    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
    (abstract.south) edge node{$(\phi(K), \vec{k})$} (synth.north)
    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge[left,xshift=-3cm] node {$K$} ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),\vec{k})$} ([xshift=-.6cm]KSAT.north)
    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
    (FAIL.north) edge (done.south)
    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
  \path[-] 
     (KSAT.south) edge (KUNSAT.north)
     (KUNSAT.east) edge (FAIL.west)
     (verify.north) edge node {$(k,x_0)$} (aux);
\end{tikzpicture}
}
\caption{Abstraction-based CEGIS.}
\label{fig:CEGARIS} 
\end{figure}

>>>>

We next evaluate $\hat{X}^\# \models \phi_\mathit{safety}$.  If the
verification holds we have a solution, and exit the loop.  Otherwise, we
find a counterexample iteration $k$ and corresponding initial point $x_0$
for which the property does not hold, which we use to locally refine the
abstraction.  When the abstraction cannot be further refined, we provide
them to the {\sc abstract} phase.
%
%\todo{we should have a better argument here.}
%\end{enumerate} 
\item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
  in which case we must refine the abstraction used by the synthesizer.
\begin{enumerate}
\item Find the constraints that invalidate the property
 as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum i.e., transfer function) of the closed loop dynamics. 
\item We use $\phi_\Lambda$ to
  further constrain the characteristic polynomial  
$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$. These constraints correspond to specific iterations for which the system may be unsafe.
\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $k$ to the {\sc synthesize} phase.
  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
\end{enumerate} 
\end{enumerate}

@@

\begin{figure}
\centering
{\scriptsize
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ 
   \&
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
      \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
   \&
   \& complexnode/.pic={
     \coordinate (UNSAT);
     \coordinate (KUNSAT)  at ([xshift=0cm]UNSAT.center);
     \node[draw=none] (UNSATB) at ([xshift=1.6cm,yshift=.3cm]UNSAT)  {\sc UNSAT\\ (No Candidate Found)};
  }
  \& \& \coordinate (FAIL);\\
  };
  \path
    (pre.east) edge node[align=center] {$P_a$, $N$,\\ $\phi_\mathit{init}^k$} (abstract.west)
    (abstract.south) edge node{$(\phi(K), k)$} (synth.north)
    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge[left,xshift=-3cm] node {$K$} ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$(\phi(K),k)$} ([xshift=-.6cm]KSAT.north)
    ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west)
    ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east)
    (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south)
    (FAIL.north) edge (done.south)
    ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
  \path[-] 
     (KSAT.south) edge (KUNSAT.north)
     (KUNSAT.east) edge (FAIL.west)
     (verify.north) edge node {$(k,x_0)$} (aux);
\end{tikzpicture}
}
\caption{Abstraction-based CEGIS.}
\label{fig:CEGARIS} 
\end{figure}
